### 2015-04-13 Dissertation/chapter-graybox.tex
Copied Comprehensive to Disseration

\subsection{Preliminary Empirical Comparison}
\begin{figure}[t]
  \begin{centering}
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{hc-time}
      \end{centering}
      \caption{Seconds per local optima.}
      \label{fig-hc-time}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{hc-radius}
      \end{centering}
      \caption{Moves in Hamming Ball}
      \label{fig-hc-radius}
    \end{subfigure}
  \end{centering}
  \caption{Comparison of performing hill climbing
           using the black box and gray box domains on Nearest Neighbor NK with $K=5$.
           Figure~\ref{fig-hc-time} shows the time required to bring a random
           solution to a local optima, averaged over 900 restarts across 30 instances.
           Figure~\ref{fig-hc-radius} shows the number of moves which must be
           tested by hill climbing when $N=500$ as $r$ increases.}
  \label{fig-hc-compare}
\end{figure}

Figure~\ref{fig-hc-time} compares the black box hill climber presented in Section~\ref{sec-hill-climber}
with the gray box hill climber presented in Section~\ref{sec-whitley-ls}.  Each algorithm was
used 30 times on each of 30 instances to improve random solutions until they reached a local optimum.
Both methods use first improvement hill climbing and achieved statistically indistinguishable fitness results.
However, the amount of time each used is drastically different. On the largest tested size of $N=8,000$ the gray box
hill climber was 800 times faster than using the black box method. This improvement was so extreme
that the gray box hill climber is able to find local optima on $N=8,000$ problems faster than the black box
method can optimize $N=400$ problems.  When compared asymptotically the black box optimizer empirically requires
$O(N^{2.14})$ time while the gray box requires $O(N)$. This matches the theoretical conclusions for both algorithms.

@@

>>>>

\subsection{Preliminary Empirical Comparison}
Figure~\ref{fig-hc-time} compares the black box hill climber presented in Section~\ref{sec-hill-climber}
with the gray box hill climber presented in Section~\ref{sec-whitley-ls}.  Each algorithm was
used 30 times on each of 30 instances to improve random solutions until they reached a local optimum.
Both methods use first improvement hill climbing and achieved statistically indistinguishable fitness results.
However, the amount of time each used is drastically different. On the largest tested size of $N=8,000$ the gray box
hill climber was 800 times faster than using the black box method. This improvement was so extreme
that the gray box hill climber is able to find local optima on $N=8,000$ problems faster than the black box
method can optimize $N=400$ problems.  When compared asymptotically the black box optimizer empirically requires
$O(N^{2.14})$ time while the gray box requires $O(N)$. This matches the theoretical conclusions for both algorithms.

@@

\begin{figure}[t]
  \begin{centering}
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{hc-time}
      \end{centering}
      \caption{Seconds per local optima.}
      \label{fig-hc-time}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \begin{centering}
        \includegraphicsfit{hc-radius}
      \end{centering}
      \caption{Moves in Hamming Ball}
      \label{fig-hc-radius}
    \end{subfigure}
  \end{centering}
  \caption{Comparison of performing hill climbing
           using the black box and gray box domains on Nearest Neighbor NK with $K=5$.
           Figure~\ref{fig-hc-time} shows the time required to bring a random
           solution to a local optima, averaged over 900 restarts across 30 instances.
           Figure~\ref{fig-hc-radius} shows the number of moves which must be
           tested by hill climbing when $N=500$ as $r$ increases.}
  \label{fig-hc-compare}
\end{figure}
